---
Title: Query encoding
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

*Taking a closer look at the query encoding issue. Eventually led to comments on [iss #335 encoding/decoding '+' as space (rather than literal '+' sign)](https://github.com/hadley/httr/issues/335) and a [pull request](https://github.com/hadley/httr/pull/337).*

Example of advanced Github search in the browser (purposefully chose example with small number of issues -- this is not about pagination):

<https://github.com/search?utf8=✓&q=type%3Aissue+author%3Ahadley+repo%3Arstudio%2Frstudioapi+state%3Aopen&type=Issues&ref=searchresults>

I see 4 issues.

Get them via API from the command line

```{r engine='bash'}
curl -o hadley-rstudioapi.json https://api.github.com/search/issues?q=type:issue+author:hadley+repo:rstudio/rstudioapi+state:open
head hadley-rstudioapi.json
```

Again, 4 issues.

How to get them from R? First, assemble all terms in a list.

```{r}
library(gh)
library(purrr)
library(httr)
suppressPackageStartupMessages(library(dplyr))

type <- "issue"
author <- "hadley"
repo <- "rstudio/rstudioapi"
state <- "open"
(search_terms <- lst(type, author, repo, state))
```

Function to create query string with `sep` between field and value and `collapse` between field-value pairs.

```{r}
make_query <- function(terms, sep = ":", collapse = " ") {
  paste(names(terms), terms, sep = sep, collapse = collapse)
}
```

Form query with `sep` set to `+` and ` `.

```{r}
(query_plus <- make_query(search_terms, collapse = "+"))
(query_space <- make_query(search_terms, collapse = " "))
```

Use `gh` with both queries.

```{r error = TRUE}
## space works
res <- gh("/search/issues", q = query_space, .limit = Inf) 
res$total_count
#jsonlite::toJSON(res$items[[1]], pretty = TRUE, auto_unbox = TRUE)

## `+` does not work
res <- gh("/search/issues", q = query_plus, .limit = Inf) 
```

Use `httr` with both queries.

```{r error = TRUE}
## space works if passed through modify_url
(url <- modify_url("https://api.github.com", path = "search/issues", 
                   query = list(q = query_space)))
x <- GET(url)
status_code(x)
length(content(x)$items)

## `+` does not work when passed through modify_url
(url <- modify_url("https://api.github.com", path = "search/issues", 
                   query = list(q = query_plus)))
x <- GET(url)
status_code(x)

## space used literally does not work, of course
(url <- paste0("https://api.github.com/search/issues?q=", query_space))
x <- GET(url)
status_code(x)

## `+` used literally does work
(url <- paste0("https://api.github.com/search/issues?q=", query_plus))
x <- GET(url)
status_code(x)
length(content(x)$items)
```
