---
output: github_document
---

Here's what we're trying to match via API:

<https://github.com/issues?q=is%3Aissue+author%3Atimelyportfolio+is%3Aopen>

I see 194 open issues.

Here's the relevant API endpoint:

<https://developer.github.com/v3/search/#search-issues>

You can't just provide the search terms as params to `gh()`. They need to be pre-processed.

```{r}
library(gh)

search_q <- list(author = "timelyportfolio", is = "open")
(search_q <- paste(names(search_q), search_q, sep = "=", collapse = "+"))
## this causes us to get an empty list !?!
## (search_q <- paste(names(search_q), search_q, sep = ":", collapse = "+"))
## (search_q <- URLencode(search_q, reserved = TRUE))
x <- gh("/search/issues", q = search_q, .limit = Inf)
str(x, max.level = 1)
length(x$items)
```

The actual issues appear in `items`. But I only get 14! A far cry from 194.

The structure of what's returned is problematic (`total_count`, `incomplete_results`, `items`) and won't play well with `gh`'s approach to de-pagination. But since we get a ridiculously small number of results, we aren't able to see that problem yet here. It almost feels like the search terms mean something different via API vs browser?

What if I try one of the search examples from the API docs? Basically success. We do seem to retrieve the relevant results and we get a demo of how the search results don't play well with `gh`'s pagination.

```{r}
search_q <- list(label = "bug", language = "python", state = "open")
search_q <- c("windows", paste(names(search_q), search_q, sep = "="))
(search_q <- paste(search_q, collapse = "+"))
x <- gh("/search/issues", q = search_q, .limit = Inf)
str(x, max.level = 1)
length(x)
```

